%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage[colorlinks,allcolors=blue]{hyperref}

\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{Richard Evans\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf Work Address} \\ VA Center for Clinical Management Research \\ 2800 Plymouth Rd Building 16 \\ Ann Arbor, MI  \\ Richard.Evans8@va.gov} % Your address 1

\address{{\bf Permanent Address} \\ 6349 Hague Ave. \\ Jackson, MI 49201 \\ (248) 910-3441 \\ revans.evans@gmail.com} % Your address 2

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} 

\vspace{8pt} % Gap between title and text

{\sl Master of Science}, Biostatistics  \hfill Sept. 2014 -  May 2016\\ 
University of Michigan School of Public Health  \\
Ann Arbor, MI

{\sl Bachelor of Science}, Biological Sciences  \hfill January 2009 - May 2012\\
Wayne State University \\
Detroit, MI

%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PROFESSIONAL EXPERIENCE}} 

\vspace{8pt}

{\sl Data Scientist} \hfill April 2018 - \\
Center for Clinical Management Research \\
VA Ann Arbor Medical Center \\
U.S. Dept. of Veteran's Affairs, Ann Arbor, MI
\begin{itemize}
    \item Data management, analysis and statistical programming for a wide variety of research and operations projects:
    \begin{itemize}
	\item Data-drive Care for Evaluation and Prevention (DCEP) (\href{https://www.academyhealth.org/node/17955}{P.I. Laura Damschroder, MS, MPH})
           \item \href{https://clinicaltrials.gov/ct2/show/NCT02360293}{Stay Strong: A Physical Activity Program for Afghanistan and Iraq Veterans} (\href{https://www.academyhealth.org/node/17955}{P.I. Laura Damschroder, MS, MPH})
	\item Structures and Processes of Pre-Surgical Care (\href{https://www.uofmhealth.org/profile/4123/erika-davis-sears-md}{P.I. Erika Sears, MD MS})
    \end{itemize}
    \item Program implementation research using \href{http://compasss.org/}{Qualitative Comparative Analyses}
    \item Lead educational workshops focusing on data and methods relevant to VA projects and commonly encountered research objectives
    \item Provide statistical consulting and database support to junior colleagues
\end{itemize}

{\sl Statistician Intermediate} \hfill May 2016 -  March 2018\\
University of Michigan School of Public Health \\
Dept. of Epidemiology, Ann Arbor, MI
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Collaborated with \textbf{Center of Disease Control and Prevention} (CDC) to perform\\
analytical programming, data management, quality control and reporting for Influenza\\ vaccination effectiveness research projects (\href{https://sites.google.com/a/umich.edu/hive/home/umsph}{\textbf{HIVE}}, \textbf{HAIVEN}, \href{https://www.cdc.gov/flu/professionals/vaccination/effectiveness-studies.htm}{\textbf{US Flu VE}}) under investigators \href{https://sph.umich.edu/faculty-profiles/monto-arnold.html}{\textbf{Arnold Monto}} and \href{https://sph.umich.edu/faculty-profiles/martin-emily.html}{\textbf{Emily Martin}}
\item Interpreted analyses for methods sections in abstracts, grants and manuscripts 
\item Using simulations implemented in \textbf{R} and other software, derived sample size and power estimates for \textbf{NIH} and \textbf{CDC} grant applications 
\item Provided statistical consulting and database support to graduate students 
\end{itemize}

{\sl Graduate Research Assistant} \hfill September 2014 - April 2016 \\
University of Michigan School of Public Health \\
Dept. of Epidemiology, Ann Arbor, MI
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Aided in infectious disease research under the direction of \href{https://sph.umich.edu/faculty-profiles/martin-emily.html}{\textbf{Prof Emily Martin}}
\item Built and managed databases in \textbf{REDCap} software and Excel
\item Prepared reports descrbing statistical analyses, presenting findings to study investigators
\item Consulted statistical literature to address research hypotheses
\item Performed literature review and data collection for meta-analyses regarding the risk of surgical infections in Diabetics
\end{itemize}
 
{\sl Research Associate} \hfill June 2015 - October 2015 \\
University of Michigan \\
Dept. of Psychiatry, Ann Arbor, MI
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Provided data management and statistical analyses for the CDC-funded randomized controlled prevention study, Links to Enhancing Teens’ Connectedness, \href{http://sites.lsa.umich.edu/king-lab/research/}{\bf{LET'S CONNECT}}, led by \href{http://www.psych.med.umich.edu/profile/?linkid = King}{\textbf{Dr. Cheryl King}}
\item Performed internal consistency analysis of psychometric tests and hierarchical modelling of survey results
\end{itemize}

{\sl Research Assistant} \hfill Mar 2013 - August 2014 \\
Wayne State University \\
College of Pharmacy and Health Sciences, Detroit, MI
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Medical chart audit and data collection for \textbf{Pfizer} and \textbf{NIH} funded retrospective and prospective pharmacoepidemiology studies
\item Queried and analyzed large (20 billion record, 1000+ variable) medical insurance claims (\href{http://truvenhealth.com/markets/life-sciences/products/data-tools/marketscan-databases}{\textbf{MarketScan}}\textsuperscript{TM}) and healthcare databases in SAS and Stata
\item Co-wrote abstracts, posters, and manuscripts for scientific conferences and journals
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	WEBSITES
%----------------------------------------------------------------------------------------

\section{\centerline{WEBSITES}} 

\vspace{15pt}
\begin{itemize}
    \item LinkedIn:  \href{https://www.linkedin.com/in/rich-evans/}{\bf rich-evans}
    \item Github: \href{https://github.com/rrevansUM}{\bf rrevansUM}
    \item Bookdown: \href{https://rrevansum.github.io/}{\bf rrevansum.github.io}
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PUBLICATIONS}} 

\vspace{10pt}

\subsection{Peer-Reviewed Articles} 

\vspace{5pt}

Arnold S Monto, Ryan E Malosh, \textbf{Richard Evans}, Adam S Lauring, Aubree Gordon, Mark G Thompson, Alicia M Fry, Brendan Flannery, Suzanne E Ohmit, Joshua G Petrie, Emily T Martin, HIVE Study Research Staff, Data resource profile: Household Influenza Vaccine Evaluation (HIVE) Study, International Journal of Epidemiology, Volume 48, Issue 4, August 2019, Pages 1040–1040g, https://doi.org/10.1093/ije/dyz086

\vspace{5pt}

Buis LR, McCant FA, Gierisch JM, Bastian LA, Oddone EZ, Richardson CR, Kim HM, \textbf{Evans R}, Hooks G, Kadri R, White-Clark C, Damschroder LJ. Understanding the Effect of Adding Automated and Human Coaching to a Mobile Health Physical Activity App for Afghanistan and Iraq Veterans: Protocol for a Randomized Controlled Trial of the Stay Strong Intervention. JMIR Res Protoc 2019;8(1):e12526; URL: https://www.researchprotocols.org/2019/1/e12526; DOI: 10.2196/12526; PMID: 30694208; PMCID: 6371069

\vspace{5pt}

Fitzsimmons WJ, Woods RJ, McCrone JT, Woodman A, Arnold JJ, Yennawar M, et al. (2018) A speed–fidelity trade-off determines the mutation rate and virulence of an RNA virus. PLoS Biol 16(6): e2006459. https://doi.org/10.1371/journal.pbio.2006459

\vspace{5pt}

Segaloff, HE,\textbf{Evans, R}, Arshad, S, et al. The impact of obesity and timely antiviral administration on severe influenza outcomes among hospitalized adults. J Med Virol. 2018; 90: 212– 218. https://doi.org/10.1002/jmv.24946

\vspace{5pt}

Sutcliffe K, Kilgore PE, DeHoff K, \textbf{Evans R}, Kaye KS, Malosh RE, Sherwin R, Martin ET. Survey of vaccination knowledge and acceptance among adults admitted to an urban emergency department. Vaccine. 2017 Feb 22;35(8):1148-1151

\vspace{5pt}

\textbf{Evans R}, Loeb A, Kaye KS, Cher ML, Martin ET. Infection-Related Hospital Admissions After Prostate Biopsy in United States Men. Open Forum Infect Dis. 2017 Jan 13;4(1):ofw265 PMID: 28480258

\vspace{5pt}

Navalkele B, Pogue JM, Karino S, Nishan B, Salim M, Solanki S, Pervaiz A,
Tashtoush N, Shaikh H, Koppula S, Koons J, Hussain T, Perry W, \textbf{Evans R}, Martin ET, Mynatt RP, Murray KP, Rybak MJ, Kaye KS. Risk of Acute Kidney Injury in Patients on Concomitant Vancomycin and Piperacillin/tazabactam Compared to Those on Vancomycin and Cefepime. Clinical Infectious Diseases. 2016 Oct 20.

\vspace{5pt}

Martin ET, Kaye KS, Knott C, Nguyen H, Santarossa M, \textbf{Evans R}, Beltran E, Jaber L. Diabetes and Risk of Surgical Site Infection: A systematic review and meta-analysis. Infection Control \& Hospital Epidemiology. 2016 Jan;37(1):88-99.

%----------------------------------------------------------------------------------------
%	ABSTRACTS AND POSTERS SUBSECTION
%----------------------------------------------------------------------------------------

\subsection{Abstracts, Posters, Seminars} 

\vspace{10pt}

Hanslits K, \textbf{Evans R}, Konja M, Sutcliffe K, Kim J, Salim M, Salzman E, Kaye KS,
Martin ET. Risk factors for MRSA-VRE coinfection among hospitalized adult.
IDWeek 2016. New Orleans, Louisiana.

\vspace{5pt}

Martin ET, \textbf{Evans R}, Compton M, Pogue JM, Lephart P, Rybak MJ, Kaye KS,
Davis SL. All-cause readmission following treatment with linezolid for MRSA-
ABSSSI: a propensity score analysis. Poster Presentation. IDWeek 2015, San
Diego, CA.

\vspace{5pt}

Martin ET, \textbf{Evans R}, Archer C, Petrie J, Arshad S, Kaye KS. Influenza, obesity and
timely administration of oseltamivir: a prospective study of patient outcomes. Poster
Presentation. IDWeek 2015, San Diego, CA.

\vspace{5pt}

\textbf{Evans R}, Archer C, Jaber L, Kaye KS, Rybak M, Davis SL, Martin ET. Epidemiology
of Polymicrobial Infections in Methicillin Resistant Staphylococcus aureus
Associated Complicated Skin and Soft Tissue Infections (Poster). Society for
Epidemiologic Research Annual Meeting, 2014. Seattle, Washington.

\vspace{5pt}

Martin ET, Compton M,  \textbf{Evans R}, McRoberts JP, Arrabi L, Pasha A, Lephart P,
Rybak MJ, Kaye KS. Molecular Epidemiology of MRSA and VRE Co-colonization
among Hospitalized Adults in Detroit (Poster). IDWeek. 2014. Philadelphia PA.

\vspace{5pt}

\textbf{Evans R}, Loeb A, Cher ML, Kaye KS, Martin ET. Infection-related Hospital
Readmissions Following Prostate Biopsy in United States Men (Poster). IDWeek.
2014. Philadelphia, PA.

\vspace{5pt}

Martin ET, McRoberts JP, Divekar P,  \textbf{Evans R}, Hill B, Archer C, Kaye KS, Rybak,
MJ. Prevalence of pSK41 plasmid among patients with MRSA and VRE dual
infection. 53rd Interscience Conference on Antimicrobial Agents and Chemotherapy
(Poster). 2013. Denver, Colorado.

\vspace{10pt}

Archer C,  \textbf{Evans R}, Davis SL, Pogue JM, Rybak MJ, Kaye KS, Martin ET.
Decreasing MRSA prevalence among ABSSSI-associated hospitalization in the
Detroit Metropolitan area, 2006-2012. 53 nd Interscience Conference on Antimicrobial
Agents and Chemotherapy (Poster). 2013. Denver, Colorado.

\vspace{5pt}

Martin ET, Archer C, \textbf{Evans R}, Biedron C, Collins V, McRoberts JP, Thurston T, Kulik J, Arshad S, Kilgore P, Kaye KS. Influenza and Obesity: A prospective study of patient outcomes and antiviral resistance (Poster). American Association of Colleges of Pharmacy Annual Meeting: Pharmacy Education 2013. Chicago, IL.

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{COMPUTING}}

\vspace{8pt}

\textbf{Analytic Software}

\textbf{Adept:} \\
R \textbullet{} Rstudio \textbullet{} SAS \\ 
\textbf{Proficient:} \\
STAN \\
\textbf{Familiar:} \\
C++ \textbullet{} Python \textbullet{} Stata \\
SPSS \textbullet{} MATLAB \textbullet{} Simulink

\textbf{Database Software}

SQL \textbullet{} mySQL \\
Access \textbullet{} Excel \\
REDCap

\textbf{Reporting Software}

\LaTeX \\
R Markdown (slides, HTML, PDF) \\
Microsoft Office Suite

%----------------------------------------------------------------------------------------

\end{resume} 
\end{document}